---
title: "Assignment 2--R"
author: "Insert your name here"
date: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Control flow:  Airport statistics

If your code uses any libraries, load them here.
```{r}
library(readr)
```

a. Download the data set `airport.csv`.  Read it into R and display the first few lines of data.

```{r}
airport = read_csv("airport.csv")
head(airport)
```

This data set contains data on all 135 medium and large airports in the US in 1990.  

(Dataset:  "US Airport Statistics," submitted by Larry Winner, University of Florida.   Dataset obtained from the Journal of Statistics Education (http://www.amstat.org/publications/jse). Accessed 3 June 2015. Used by permission of author.) 

b. **Use control flow** to print a list of airports at which the number of scheduled departures was less than the number of departures performed.

- The point of this assignment is to demonstrate your understanding of control flow, so please use control flow to solve this problem.

```{r}
numRows = dim(airport)[1]
for(airport_index in 1:numRows) {
  if(airport[airport_index, 3] < airport[airport_index, 4]){
     print(as.character(airport[airport_index, 1]))
  }
}
```



c. **Use control flow** to find the average (mean) number of passengers on flights from all the airports in part b.

- Your result should be 1 number:  The total number of passengers from all of the specified airports, divided by the total number of performed departures from all of the specified airports.

- The point of this assignment is to demonstrate your understanding of control flow, so please use control flow to solve this problem.

```{r}
for(airport_index in 1:numRows) {
  if(airport[airport_index, 3] < airport[airport_index, 4]){
     for(airport_index in 1:numRows) {
       passengers = sum(airport$Passengers)
       departures = sum(airport$`Performed Departures`)
      }
  }
}

result = passengers/departures
print(result)                        
noPartialPeople = floor(result)      
print(noPartialPeople)          
```
NOTE: I've displayed the exact value and the value rounded down to the nearest whole person. I feel like both are 'correct' in their own way, depending on the nature of the problem.
      I'm including both in my assignment submission to demonstrate that I got the exact answer but am adding the rounded answer in case it was something I was supposed to catch.
      
      
d.  Optional: 	If you know a more efficient way to do parts b and c in R, that's great!  Do that here and use the result to check your work.  (If you don't know a more efficient way, that's fine.  We'll discuss methods of writing efficient code later in the course.)
```{r}

```


-	Submit your .Rmd file and knitted .pdf or .docx file (.pdf preferred) to GitHub.
